Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-02-17 MS_revised.tex
refix captions supp mat

\section*{Supporting Information Legends}
\textbf{S1 Figure.
\bf Boxplot of speciation (\(\lambda\)) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.}

\textbf{S2 Figure.
BiSSE analysis of diversification of nymphalids
due to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders}. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders \(\lambda1\), r1).

\textbf{S3 Figure.
Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution}.

\textbf{S4 Figure.
Boxplot of speciation and extinction values for
the 95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.}

\textbf{S5 Figure.
BiSSE analysis of diversification of nymphalids
due to feeding on Apocynaceae hostplants}. Speciation and net
diversification rates are similar.

\textbf{S6 File.
1000 random trees from \cite{wahlberg2009}}.

\textbf{S7 Dataset.
Species richness for lineages in Nymphalidae}.

\textbf{S8 Dataset.
Hostplants of Nymphalidae
butterflies recorded from the literature}.

\textbf{S9 Dataset.
References for hostplants data}.

\textbf{S10 File.
R script to run MEDUSA on the MCC Nymphalidae tree from
\cite{wahlberg2009}}. This script removes the outgroup
taxa and loads the richness data for the tree terminals.

\textbf{S11 File.
R script to run a MultiMEDUSA analysis on 1000 random trees from
\cite{wahlberg2009}}.

\textbf{S12 Supporting Information.
R script to run a MEDUSA
analysis on the MCC tree from the 1000 random trees selected from the
posterior distribution}.

\textbf{S13 Dataset.
Data matrix with character states for hosplant use}.

\textbf{S14 Supporting Information.
MCC tree from the 1000 random
trees selected from the posterior distribution}.

\textbf{S15 File.
Raw results from the MultiMEDUSA run on the random sample of trees from 
the posterior distribution}.

\textbf{S16 Text.
Summary results from a
MultiMEDUSA run on the 1000 random trees selected from the posterior
distribution}.

\textbf{S17 Figure.
Probability of nodes with
estimated rates from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution}.

\textbf{S18 Supporting Information.
R script for running the BiSSE analysis}.

\textbf{S19 Supporting Information.
Raw results for the BiSSE analysis}.

\textbf{S20 Supporting Information.
Raw results for the combined BiSSE analysis}.

\textbf{S21 Dataset.
MCC Nymphalidae tree from \cite{wahlberg2009}}

\textbf{S22 Text.
Results of running MEDUSA on the MCC tree}.

\textbf{S23 Figure.
Summary of the MultiMEDUSA
analysis on the 1000 trees from the posterior distribution}.

\textbf{S24 Text.
Summary results from a MEDUSA
run on the MCC tree from the 1000 random trees selected from the
posterior distribution}.

\textbf{S25 Figure.
Figure for MEDUSA run on MCC tree from random 1000 trees}.

>>>>

\section*{Supporting Information}

\subsection*{S1 Figure}
\label{S1_Figure}
{\bf Boxplot of speciation (\(\lambda\)) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.}

\subsection*{S2 Figure}
\label{S2_Figure}
{\bf BiSSE analysis of diversification of nymphalids
due to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders}. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders \(\lambda1\), r1).

\subsection*{S3 Figure}
\label{S3_Figure}
{\bf Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution}.

\subsection*{S4 Figure}
\label{S4_Figure}
{\bf Boxplot of speciation and extinction values for
the 95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.}

\subsection*{S5 Figure}
\label{S5_Figure}
{\bf BiSSE analysis of diversification of nymphalids
due to feeding on Apocynaceae hostplants}. Speciation and net
diversification rates are similar.

\subsection*{S6 File}
\label{S6_File}
{\bf 1000 random trees from \cite{wahlberg2009}}.

\subsection*{S7 Dataset}
\label{S7_Dataset}
{\bf Species richness for lineages in Nymphalidae}.

\subsection*{S8 Dataset}
\label{S8_Dataset}
{\bf Hostplants of Nymphalidae
butterflies recorded from the literature}.

\subsection*{S9 Dataset}
\label{S9_Dataset}
{\bf References for hostplants data}.

\subsection*{S10 File}
\label{S10_File}
{\bf R script to run MEDUSA on the MCC Nymphalidae tree from
\cite{wahlberg2009}}. This script removes the outgroup
taxa and loads the richness data for the tree terminals.

\subsection*{S11 File}
\label{S11_File}
{\bf R script to run a MultiMEDUSA analysis on 1000 random trees from
\cite{wahlberg2009}}.

\subsection*{S12 Supporting Information}
\label{S12_Supporting_Information}
{\bf R script to run a MEDUSA
analysis on the MCC tree from the 1000 random trees selected from the
posterior distribution}.

\subsection*{S13 Dataset}
\label{S13_Dataset}
{\bf Data matrix with character states for hosplant use}.

\subsection*{S14 Supporting Information}
\label{S14_Supporting_Information}
{\bf MCC tree from the 1000 random
trees selected from the posterior distribution}.

\subsection*{S15 File}
\label{S15_File}
{\bf Raw results from the MultiMEDUSA run on the random sample of trees from 
the posterior distribution}.

\subsection*{S16 Text}
\label{S16_Text}
{\bf Summary results from a
MultiMEDUSA run on the 1000 random trees selected from the posterior
distribution}.

\subsection*{S17 Figure}
\label{S17_Figure}
{\bf Probability of nodes with
estimated rates from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution}.

\subsection*{S18 supporting information}
\label{S18_Supporting_Information}
{\bf R script for running the BiSSE analysis}.

\subsection*{S19 Supporting Information}
\label{S19_Supporting_Information}
{\bf Raw results for the BiSSE analysis}.

\subsection*{S20 Supporting Information}
\label{S20_Supporting_Information}
{\bf Raw results for the combined BiSSE analysis}.

\subsection*{S21 Dataset}
\label{S21_Dataset}
{\bf MCC Nymphalidae tree from \cite{wahlberg2009}}

\subsection*{S22 Text}
\label{S22_Text}
{\bf Results of running MEDUSA on the MCC tree}.

\subsection*{S23 Figure}
\label{S23_Figure}
{\bf Summary of the MultiMEDUSA
analysis on the 1000 trees from the posterior distribution}.

\subsection*{S24 Text}
\label{S24_Text}
{\bf Summary results from a MEDUSA
run on the MCC tree from the 1000 random trees selected from the
posterior distribution}.

\subsection*{S25 Figure}
\label{S25_Figure}
{\bf Figure for MEDUSA run on MCC tree from random 1000 trees}.
